An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2011-04-05 paper.tex
Wording change on Littenberg and Cornish intro reference.

\IfFileExists{revtex4-1.cls}{\documentclass[prd, twocolumn, lengthcheck,
superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4-1}}{ 
\IfFileExists{revtex4.cls}{\documentclass[prd, preprint,
superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4}}{}
}

@@

@@

Implemented naively, RJMCMC has a significant drawback: because the
chain of samples must be Markovian, only the current sample is
available to the algorithm as it is choosing the next sample.  Each
time an RJMCMC transitions between models, the information about the
choices of parameter values in the previous model is lost; subsequent
jumps into that model must ``start fresh,'' and are correspondingly
unlikely to be accepted, delaying convergence of the RJMCMC sample
chain.  One of the first papers to address this issue was Reference
\cite{Littenberg2009}, where the authors propose a method for
producing inter-model jumps in an RJMCMC that relies on interpolating
single-model posterior distributions using a box decomposition of
parameter space.

>>>>

\IfFileExists{revtex4-1.cls}{\documentclass[prd, reprint,
superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4-1}}{ 
\IfFileExists{revtex4.cls}{\documentclass[prd,
superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4}}{}
}

@@

\pacs{02.70.Tt, 95.75.Pq, 07.05.Kf}

@@

Implemented naively, RJMCMC has a significant drawback: because the
chain of samples must be Markovian, only the current sample is
available to the algorithm as it is choosing the next sample.  Each
time an RJMCMC transitions between models, the information about the
choices of parameter values in the previous model is lost; subsequent
jumps into that model must ``start fresh,'' and are correspondingly
unlikely to be accepted, delaying convergence of the RJMCMC sample
chain.  Reference \cite{Littenberg2009} addressed this issue by
proposing a new method for producing inter-model jumps in an RJMCMC
that relies on interpolating single-model posterior distributions
using a box decomposition of parameter space.
